### 2019-09-20 proglog.tex
added workshop information

@@

\subsubsection{Scientific Writing Workshop}

\subsubsection{LaTeX Workshop}

>>>>

\subsubsection{Building Your Network}
The AAAS conducts workshops that teach early career scientists and students how to develop a professional network that will benefit them in the future. They hold regular workshops about strategic networking, making new contacts, and getting the most out of a conference. We will invite them to conduct a workshop where attendees can come away with skills to maximize their experience at the ANS Student Conference.

@@
